Agreement Attraction in Turkish\\ \bigskip \large Word count: \Sexpr{count}

### 2021-07-06 paper/glossa/glossa-template-knitr.Rnw
anonimized links

% see http://info.semprag.org/basics for a full description of this template
%\documentclass[linguex]{glossa}
% DO NOT FORGET TO setwd("paper/glossa/") where the Rnw file is.
\documentclass[brill,linguex]{glossa}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

@@

\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish\\ \bigskip \large Word count: 2,749}
% Optional short title inside square brackets, for the running headers.

\author[A.B. \& C.D.]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
{%as many authors as you like, each separated by \AND.
  \spauthor{\texttt{Hidden Hidden (A.B.)}\\ 
  \institute{\texttt{Hidden University}}\\
  \small{
    \texttt{hidden@hidden.edu}}
  }
  \AND
  \spauthor{\texttt{Hidden Hidden (C.D.)}\\ 
  \institute{\texttt{Hidden University}}\\
  \small{
    \texttt{hidden@hidden.edu}}
  }%
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

We recruited 118 undergraduate students to participate in the experiment in exchange for course credit. All participants were native Turkish speakers, with an average age of 20 (range: 18 -- 32). The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at \texttt{Hidden University}. All participants provided informed consent before their participation and their identity are completely anonimized.

@@

Prior to the analysis, we removed the data for all participants who failed to show sufficient sensitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected. Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between the grammatical condition \ref{ex:expitem-sgsg} and the ungrammatical condition \ref{ex:expitem-sgpl} fell below the threshold of 0.25 percentage points. We also excluded trials in which the participants missed the response deadline or gave too fast responses (below 200 ms). As a result, we excluded 10.22\% of the trials from our experiment and 2.38\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.

@@

In the results section, we provide posterior distributions for parameters given our data and model with 95\% credible intervals. For our models, we run 4 chains, each of which consists of 1000 warm-up iterations and 1000 sampling iterations. Data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.

@@

Figure \ref{fig:AverageResponses} shows the average proportions of `acceptable' responses by experimental condition for both the original experiment in \citet{LagoEtAl:2019} and our replication with unambiguous possessive marking. It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = 0.22, SE = 0.01) than their counterparts with singular attractors (M = 0.11, SE=0.01). The magnitude of the effect (0.11) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was 0.11. Accuracy rates for grammatical conditions were nearly equal (M = 0.93 and 0.92, SE = 0.01 and 0.01, for singular and plural attractors respectively).

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/AverageResponses-1}

}

\end{knitrout}

@@

Figure \ref{fig:ResponseModel} shows estimates and 95\% credible intervals of a Bayesian GLM with a probit link function. The main effect of grammaticality ($\hat{\beta}=3.08;$ $CI=[2.84; 3.33];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences. Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.04; -0.42];$ $P(\beta<0)> .999$) indicated a more prominent effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect. There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.27;$ $CI=[-0.77; 0.25];$ $P(\beta<0)=    .85$).

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/ResponseModel-1}

}

\end{knitrout}

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/UngramResponseModel-1}

}

\end{knitrout}

@@

\begin{table}

\caption{\label{tab:unnamed-chunk-3}Point estimate, estimate error, and credible interval for Regression coefficients}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
  & Estimate & Est.Error & Q2.5 & Q97.5\\
\midrule
Intercept & -1.2216372 & 0.0897748 & -1.3990933 & -1.0491069\\
cEndsInConsonant & 0.0740791 & 0.1739013 & -0.2713538 & 0.4199774\\
cAttractorPlural & 0.4594237 & 0.0995349 & 0.2560289 & 0.6526212\\
cEndsInConsonant:cAttractorPlural & 0.0077682 & 0.1629159 & -0.3157023 & 0.3250568\\
\bottomrule
\end{tabular}
\end{table}

>>>>

% see http://info.semprag.org/basics for a full description of this template
%\documentclass[linguex]{glossa}
% DO NOT FORGET TO setwd("paper/glossa/") where the Rnw file is.
\documentclass[brill,linguex]{glossa}

@@

<<wordcount, echo=FALSE, cache=FALSE>>=
library(knitr)

comma <- function (x, ...) {
  format(x, ..., big.mark = ",", scientific = FALSE, trim = TRUE)
}

# To dynamically extract name of the current file, use code below
nameoffile <- current_input() # get name of file
nof2 <-  strsplit(nameoffile,"\\.")[[1]][1] # extract name, drop extension
noftex <- paste(nof2, ".tex", sep="") # add .tex extension
nofwordcount <-  paste(nof2, '-','wordcount', '.tex', sep = "") # prepare a tex file for word count
if (file.exists(nofwordcount)) {unlink(nofwordcount)} #delete the previous file.

con <- file(noftex, open = 'r') # open the file with R
while(TRUE) {
  line <- readLines(con, n = 1) # read lines
  if(length(line) == 0) break # pass if nothing is there
  else if(!endsWith(line, "%exclude")){ # if the line does not end with %exclude 
    write(line, file = nofwordcount, append = TRUE) # write it to the new file
  } 
}
close(con)

systemcall <- paste("system('texcount -inc -incbib -total -sum ", nofwordcount, "', intern=TRUE)", sep="") # paste together texcount system command
texcount.out <- eval(parse(text=systemcall)) # run texcount on current last compiled .tex file with edits

sum.row <- grep("Sum count", texcount.out, value=TRUE) # extract row
pattern <- "(\\d)+" # regex pattern for digits

count <- regmatches(sum.row, regexpr(pattern, sum.row) )
# extract digits

count <- comma(as.numeric(count)) # add comma

@

@@

\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish\\ \bigskip \large Word count: \Sexpr{count}}
% Optional short title inside square brackets, for the running headers.

\author[A.B. \& C.D.]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
{%as many authors as you like, each separated by \AND.
  \spauthor{\texttt{Hidden Hidden (A.B.)}\\ 
  \institute{\texttt{Hidden University}}\\
  \small{
    \texttt{hidden@hidden.edu}}
  }
  \AND
  \spauthor{\texttt{Hidden Hidden (C.D.)}\\ 
  \institute{\texttt{Hidden University}}\\
  \small{
    \texttt{hidden@hidden.edu}}
  }%
}

\begin{document}

<<include=FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE
)
@

@@

We recruited \Sexpr{n_subject} undergraduate students to participate in the experiment in exchange for course credit. All participants were native Turkish speakers, with an average age of \Sexpr{mean_age} (range: \Sexpr{min_age} -- \Sexpr{max_age}). The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at \texttt{Hidden University}. All participants provided informed consent before their participation and their identity are completely anonimized.

@@

Prior to the analysis, we removed the data for all participants who failed to show sufficient sensitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected. Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between the grammatical condition \ref{ex:expitem-sgsg} and the ungrammatical condition \ref{ex:expitem-sgpl} fell below the threshold of \Sexpr{accuracy_threshold} percentage points. We also excluded trials in which the participants missed the response deadline or gave too fast responses (below \Sexpr{rt_threshold} ms). As a result, we excluded \Sexpr{perc_deletion_exp1}\% of the trials from our experiment and \Sexpr{perc_deletion_lago}\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.

@@

In the results section, we provide posterior distributions for parameters given our data and model with 95\% credible intervals. For our models, we run \Sexpr{n_chains} chains, each of which consists of \Sexpr{n_warmup} warm-up iterations and \Sexpr{n_iter-n_warmup} sampling iterations. Data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/tr_short_agreement_attraction/}.

@@

Figure \ref{fig:AverageResponses} shows the average proportions of `acceptable' responses by experimental condition for both the original experiment in \citet{LagoEtAl:2019} and our replication with unambiguous possessive marking. It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = \Sexpr{exp1_cur_entry1$M}, SE = \Sexpr{exp1_cur_entry1$SE}) than their counterparts with singular attractors (M = \Sexpr{exp1_cur_entry2$M}, SE=\Sexpr{exp1_cur_entry2$SE}). The magnitude of the effect (\Sexpr{m_effect}) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was \Sexpr{m_effect_lago}. Accuracy rates for grammatical conditions were nearly equal (M = \Sexpr{exp1_cur_entry3$M} and \Sexpr{exp1_cur_entry4$M}, SE = \Sexpr{exp1_cur_entry3$SE} and \Sexpr{exp1_cur_entry4$SE}, for singular and plural attractors respectively).

@@

<<AverageResponses, echo=FALSE, fig.align='center', fig.height=3, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=

plot(p_avg_resp)

@

@@

Figure \ref{fig:ResponseModel} shows estimates and 95\% credible intervals of a Bayesian GLM with a probit link function. The main effect of grammaticality (\Sexpr{estimate_cGrammatical}) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences. Meanwhile, the negative interaction between grammaticality and attractor number (\Sexpr{estimate_cGrammatical_cAttractorPlural}) indicated a more prominent effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect. There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number (\Sexpr{estimate_threeway_interaction}).

@@

<<ResponseModel,  echo=FALSE, fig.align='center', fig.height=3, warning=FALSE, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=

suppressWarnings({
p_m_response
})

@

@@

\section*{Abbreviations} %exclude

\textsc{abl} = ablative, \textsc{dat} = dative, \textsc{gen} = genitive, \textsc{loc} = locative, \textsc{nmlz} = nominalizer, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular. %exclude

\section*{Data Availability} %exclude

The data that support the findings of this study, the code, and the paper resources including \LaTeX{} and \texttt{Sweave} files are openly available in the anonimized github page at \url{https://anonymous.4open.science/r/tr_short_agreement_attraction/}. %exclude

\section*{Authors' Contributions} %exclude

A.B. conceived the initial version of the presented idea. A.B. and C.D. conceived and planned the final version of the experiment. A.B. implemented and carried out the experiment and performed initial numerical calculations and Bayesian analyses of the experiment. C.D. verified the analytical methods and carried out advanced analyses including \citet{Cousineau:2007} standard errors, advanced plotting, advanced decisions in Bayesian modelling, and R workflow. A.B. took the lead in writing the draft of the manuscript and C.D. edited the draft heavily. All authors discussed the results and commented on the manuscript. C.D. supervised the whole process. %exclude

@@

<<UngramResponseModel,  echo=FALSE, fig.align='center', fig.height=3, warning=FALSE, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=

suppressWarnings({
p_m_ungram_response
})

@

@@

<<echo=FALSE, warning=FALSE, message=FALSE>>=
library(knitr)
dat <- tables$results_table_ungram_responses
options(knitr.table.format = "latex")
@

<<results='asis', echo=FALSE, warning=FALSE, message=FALSE>>=
kable(dat, booktabs=TRUE, caption="Point estimate, estimate error, and credible interval for Regression coefficients")
@

### 2021-07-06 paper/glossa/glossa-template-knitr.tex
anonimized links

\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish\\ \bigskip \large Word count: 2,749}
% Optional short title inside square brackets, for the running headers.

@@

In the results section, we provide posterior distributions for parameters given our data and model with 95\% credible intervals. For our models, we run 4 chains, each of which consists of 1000 warm-up iterations and 1000 sampling iterations. Data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.

>>>>

\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish\\ \bigskip \large Word count: 2,759}
% Optional short title inside square brackets, for the running headers.

@@

In the results section, we provide posterior distributions for parameters given our data and model with 95\% credible intervals. For our models, we run 4 chains, each of which consists of 1000 warm-up iterations and 1000 sampling iterations. Data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/tr_short_agreement_attraction/}.

### 2021-07-06 paper/glossa/glossa-template.Rnw
anonimized links

<<include=FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE
)
@

@@

<<AverageResponses, echo=FALSE, fig.align='center', fig.height=3, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=

@@

<<ResponseModel,  echo=FALSE, fig.align='center', fig.height=3, warning=FALSE, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=

@@

<<UngramResponseModel,  echo=FALSE, fig.align='center', fig.height=3, warning=FALSE, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=

>>>>

\SweaveOpts{concordance=TRUE}

@@

<<AverageResponses, echo=FALSE, fig.align='center', height=3, dev=cairo_pdf, png=TRUE, dpi = 300, message=FALSE>>=

@@

<<ResponseModel,  echo=FALSE, fig.align='center', height=3, warning=FALSE, dev = cairo_pdf, png=TRUE, dpi = 300, message=FALSE>>=

@@

<<UngramResponseModel,  echo=FALSE, fig.align='center', height=3, warning=FALSE, dev = cairo_pdf, png=TRUE, dpi = 300, message=FALSE>>=
